Title of my paper

### 2013-03-02 paper.tex
more

\usepackage[utf8]{inputenc}
\usepackage{amsthm,amssymb,amsmath,dsfont,mathrsfs,nicefrac}
\usepackage{listings}

\let\stdsection\section
\renewcommand\section{\newpage\stdsection}

@@

% It is not possible
It is clear that not all sentences can be unambigiously translated from natural language to logic. A sentence like 	
\begin{quotation}
A farmer beats a donkey
\end{quotation}
Might be translated as 
\begin{equation}
\exists x ( farmer(x) \wedge \exists y ( donkey(y) \wedge beats(x,y)))
\end{equation}
Indicating that ``a farmer'' refers to some specific individual. Or we can might see it as a general rule, and translate it as
\begin{equation}
\forall x ( farmer(x) \rightarrow \exists y ( donkey(y) \wedge beats(x,y)))
\end{equation}
Indicating that every farmer has some donkey he beats. Or we could even read it as
\begin{equation}
\exists y ( donkey(y) \wedge \forall x ( farmer(x) \rightarrow beats(x,y)))
\end{equation}
Indicating that the poor donkey is common between all farmers.

@@

\section{Formal Stuff}
10 pagish
This subsection's content...
\subsection{DPL}
Dynamic semantics: http://plato.stanford.edu/entries/dynamic-semantics/
This subsection's content...
\subsection{Using the monad}
This might be what I call DRA underneath
\subsection{DRA}
This might be just the same as DPL
\subsection{Dependencies}
This subsection's content...
\subsection{Montague semantic}
This subsection's content...
\subsection{Semantics via dependencies}
This subsection's content...

>>>>

\usepackage[utf8]{inputenc}
\usepackage{amsthm,amssymb,amsmath,dsfont,mathrsfs,nicefrac,wasysym}
\usepackage{listings}
\let\stdsection\section
\renewcommand\section{\newpage\stdsection}

@@

% It is not possible
It is clear that not all sentences can be unambigiously translated from natural language to logic. A sentence like 	
\begin{quotation}
A farmer beats a donkey
\end{quotation}
Might be translated as 
\begin{equation}
\exists x ( farmer(x) \wedge \exists y ( donkey(y) \wedge beats(x,y)))
\end{equation}
Indicating that ``a farmer'' refers to some specific individual. Or we can might see it as a general rule, and translate it as
\begin{equation}
\forall x ( farmer(x) \rightarrow \exists y ( donkey(y) \wedge beats(x,y)))
\end{equation}
Indicating that every farmer has some donkey he beats. Or we could even read it as
\begin{equation}
\exists y ( donkey(y) \wedge \forall x ( farmer(x) \rightarrow beats(x,y)))
\end{equation}
Indicating that the poor donkey is common between all farmers.
% This seams wrong to me

@@

\section{Formal Stuff}
10 pagish
This subsection's content...
\subsection{DPL}
Dynamic semantics: http://plato.stanford.edu/entries/dynamic-semantics/

growth of information in time
Inspired by programming language
not philosofically, states can be anything. I don't want to get into that
isomorphic with normal logic (visser siger generalization/projection)
doen't promise to be a perfect dual of natural language, but it's closer, and has been rewarding
Dynamic semantics aims to model meaning and interpretation. You can do that without answering broader philosophical questions
takes the meaning of concepts for given
discourse representation theory, file change, update semantics, 
Hans Kamp, Veltman, Groenendijk

compoitionality. A man comes in. He sees a dog. He smiles.

Vi har brug for en logik, der ikke behøver at vide alting fra starten

direct translation not possible
`He saw the man with the telescope'
and even if we understand the syntax
`The students all attended one class'
has at least two meanings.
interpretation of discourse is influenced and guided by the common ground that exists between speaker and hearer

relation between sets of assignments
$\{\overline{PQR}, \overline{PQ}R, \overline{P}Q\overline{R}, \overline{P}QR, P\overline{QR}, P\overline{Q}R, PQ\overline{R}, PQR\}$

example

real world example

something about more information, less models
the interpretation of false

Something about kleiski combinator?

the thing about quantifiers
how they would work in a programming language
$\exists x; A$
$\exists x; x = 4$ hvis $x=4$ skal virke og reducere mængden af modeller, så må exists gøre dem alle sammen mulige

A man comes in. En fri variabel vi ikke ved noget om.
A man comes in. It's Thomas..

we take as DPL-meanings binary relations between assignments

later we will use an isomorphism and take them as functions from assignments to sets of assignments.

\begin{equation}
\phi ::= \bot \mid \top \mid \pi \mid \epsilon \mid \phi \cdot \phi \mid \lnot(\phi)
\end{equation}
\begin{equation}
\alpha [\bot] \beta :\equiv False
\end{equation}
\begin{equation}
\alpha [\top] \beta :\equiv \alpha = \beta
\end{equation}
\begin{equation}
\alpha[P(x_0, ..., xn-1)]\beta :\equiv \alpha = \beta and (\alpha x0, ..., \alpha x n-1 ) \in I(P)
\end{equation}

\subsection{The problem with disjunction}

a farmer doesn't own a horse or a donkey

Ex.farmer(x) . ~(Ey.horse(y).owns(x,y) v Ey.donkey(y).owns(x,y))
Ex.farmer(x) . ~Ey.horse(y).owns(x,y) . ~Ey.donkey(y).owns(x,y)

a farmer beats a horse or a donkey

Ex.farmer(x).(Ey.horse(y) v Ez.donkey(z)).beats(x,y) = {Nothing, Ex.farmer(x).EyJust .horse(y).beats(x,y)}

Ex.farmer(x).~((Ey.horse(y) v Ez.donkey(z)).beats(x,y)) =
Ex.farmer(x).(~Ey.horse(y).~Ez.donkey(z) v ~beats(x,y)) = {Nothing, Ex.farmer(x).~Ey.horse(y).~Ez.donkey(z)}

Ex.farmer(x).~(tall(x) v blue(x)) = Ex.famer(x).~tall(x).~blue(x)

There is a farmer who maybe has a donkey. He beats it.
Ex.farmer(x).(Ey.donkey(y) v false).beats(x,y)
With union semantics for v this would be equal to
Ex.farmer(x).Ey.donkey(y).beats(x,y)
which is stupid.
Intead with sets of relations, this would be equal to
Ex.farmer(x).Ey.donkey(y).beats(x,y) v Ex.farmer(x).false.beats(x,y)
the right side being an error? no

If a farmer is not poor he owns a donkey. He beats it.
Ex.farmer(x).~poor(x) -> Ey.donkey(y).owns(x,y).beats(x,y)

A farmer is either poor or he owns a donkey. He beats it.
Ex.farmer(x).(poor(x) v Ey.donkey(y).owns(x,y)).beats(x,y) =

(Ex v false) . f(x)
(exist x `union` false) [] = [[("x",0)],[("x",1)],[("x",2)]
[Nothing, Just [[("x",0)],[("x",1)],[("x",2)]]]

(Ex v false) = [Just [[("x",0)],[("x",1)],[("x",2)], Just []]
not (Ex v false) =

not (Ex v f(x))
= ~Ex.~f(x)

A farmer owns a horse or a donkey
Ex.farmer(x).~(~(Ey.horse(y)).~(Ey.donkey(y))).owns(x,y)   this surely doesn't work

nothing survives out of a not (or impl) it's normal. Don't worry about it

Let's just say that if some of 
maybe not (bla v bla v bla v ERROR) should be ERROR
it could also be something more involved, like ERROR(bla v bla v bla v ERROR), but let's not do that
fmap

\subsection{Monadic variants}
This might be what I call DRA underneath
In the previous subsection we saw that DPL allowed us to rewrite the donkey sentence as

\begin{equation}
\exists x \cdot farmer(x) \cdot \exists y \cdot donkey(y) \cdot owns(x,y) \rightarrow beats(x,y)
\end{equation}

($\cdot$ binds stronger than $\rightarrow$)

But think about the slight modification to the sentence:

\begin{quotation}
A farmer owns a donkey, if he beats it
\end{quotation}

We would have to write that as

\begin{equation}
\exists x \cdot farmer(x) \cdot \exists y \cdot donkey(y) \cdot beats(x,y) \rightarrow owns(x,y)
\end{equation}

The problem here is that reorderings like this work against our sought property of linearity: of being able to add new information as we go. We cannot compose `A farmer owns a donkey' and `if he beats it' in a meaningful way.

To resque us from this problem Albert Visser suggests constructing a special e-monoid over the dynamic relational algebra. The idea is that we are going to simultaniously work on two `streams' of dpl, and switch easily between them with a special element $\Bowtie$.

Our sentence from above will then be expressible as

\begin{equation}
\Bowtie \cdot \exists x \cdot farmer(x) \cdot \exists y \cdot donkey(y) \cdot \Bowtie \cdot owns(x,y) \Bowtie \cdot beats(x,y)
\end{equation}

This is however still not quite as close to natural language as we would like. Specially

\subsection{Dependencies}
This subsection's content...
\subsection{Montague semantic}
This subsection's content...
\subsection{Semantics via dependencies}
This subsection's content...
